Contextuality and the Born rule in fuzzy quantum theories

### 2017-04-07 prop_letter.tex
prop_letter.tex \paragraph{Quantum IVPM and Real-valued Probability Measure} Before roll-back to d=3...

Notice that $\iota_{\infty}\circ\mu_{0}$ has different core element
relative to different sub-event spaces so that it has an empty core
relative to all projectors~$\events$. When $d\ge3$, if we have
infinite measurement resource and consider $\bar{\mu}:\events\rightarrow\mathscr{I}_{\infty}$,
by Gleason's theorem, $\mathrm{core}\left(\bar{\mu},\events\right)$
has a unique element, i.e., we can always identify a unique state.
However, when we only have finite resources, we usually can only identify
a quantum IVPM to more than one states on different sub-event spaces.
The simplest example add an one extra interval~$\unknown=\left[0,1\right]$
to $\mathscr{I}_{\mathrm{D}}$, and consider $\mathscr{I}_{1}=\left\{ \imposs,\unknown,\necess\right\} $.
Then, the quantum IVPM
\begin{equation}
\bar{\mu}_{1}\left(P\right)=\begin{cases}
\necess & \text{, if }P=\mathbb{1}\text{ ;}\\
\imposs & \text{, if }P=\mathbb{0}\text{ ;}\\
\unknown & \text{, otherwise.}
\end{cases}\label{eq:homomorphism-1}
\end{equation}
provides no information about any results so that $\mathrm{core}\left(\bar{\mu}_{1},\events'\right)$
contains every density matrix. A more sophisticating example is the
following.

>>>>

Notice that $\iota_{\infty}\circ\mu_{0}$ has different core elements
relative to different sub-event spaces so that it has an empty core
relative to all projectors~$\events$. When $d\ge3$, if we have
infinite measurement resource and consider $\bar{\mu}:\events\rightarrow\mathscr{I}_{\infty}$,
by Gleason's theorem, $\mathrm{core}\left(\bar{\mu},\events\right)$
has a unique element, i.e., we can always identify a unique state.
However, when we only have finite resources, we usually can only identify
a quantum IVPM to more than one states on different sub-event spaces.
The simplest example add one extra interval~$\unknown=\left[0,1\right]$
to $\mathscr{I}_{\mathrm{D}}$, and consider $\mathscr{I}_{1}=\left\{ \imposs,\unknown,\necess\right\} $.
Then, the quantum IVPM
\begin{equation}
\bar{\mu}_{1}\left(P\right)=\begin{cases}
\necess & \text{, if }P=\mathbb{1}\text{ ;}\\
\imposs & \text{, if }P=\mathbb{0}\text{ ;}\\
\unknown & \text{, otherwise.}
\end{cases}\label{eq:homomorphism-1}
\end{equation}
provides no information about any results so that $\mathrm{core}\left(\bar{\mu}_{1},\events'\right)$
contains every density matrix. A more sophisticating example is the
following.
